Group 5 Report

### 2022-08-02 Report/Group 5 report.Rmd
endret på intro
Adding dashboard image.

@@

1. Creating KPI(s) is important for the organization’s performance 
management, to influence the objective, and to foster growth.

2. Automating the data collection will streamline the work of OPX 
and create more transparency which enhances trust in charities.

@@

@@

The dashboard also allows the user to download a pdf version of the analysis through clicking on a button. A `downloadHandler()` function passes the necessary parameters to the R Markdown document and displays a temporary notification while the file is being created. The function includes temporary file creation arguments that should enable it to function on e.g. shinyapps.io and similar server contexts, but this has not been tested.

>>>>

1. Automating the data collection will streamline the work of OPX 
and create more transparency which enhances trust in charities.

2. Creating KPI(s) is important for the organization’s performance 
management, to influence the objective, and to foster growth.

@@

@@

```{r, out.width="65%", fig.cap="The dashboard", fig.align='center', echo=FALSE}
knitr::include_graphics("Images/Dashboard_page_1.png")
```

@@

The dashboard also allows the user to download a pdf version of the analysis through clicking on a button. A `downloadHandler()` function passes the necessary parameters to the R Markdown document and displays a temporary notification while the file is being created. The function includes temporary file creation arguments that should enable it to function on e.g. [shinyapps.io](https://www.shinyapps.io/) and similar server contexts. It has been tested on shinyapps.io, but not on any private server.
